Draft

### 2024-07-08 Manuscript_draft/Draft.Rmd
Added climatic variables plot
Minor update to the draft

## Parametric model
We defined a parametric model to consider all the three effects on respiration we hypothesized. The first is the influence of temperature, then the influence of soil moisture, and then a seasonal component which is assumed to be roughly proportional to the interactions of autotrophic respiration (which we hypothesized following a seasonal pattern).
Temperature and moisture scaling interact linearly, while seasonality was assumed additive:
$$
Rh(t) =  \xi_{temp(t,j)} \cdot \xi_{moist(t,j)} \right) + \xi_{sin(t,j)}
$$

@@

### Moisture 
The moisture scaling function had to be taken from a simplified version of $Moyano.2013 in the SoilR package [@SierraMueller].
$$
\xi_{moist(t,k)}  =   a_j \cdot \theta_{v}(t) - b_j \cdot (\theta_{v}(t))^2
$$
Variance is by treatment.

@@

## Sites microclimate

@@

![Alt text](../Figures/fit_ML_validation.png)

![Alt text](../Figures/fit_model_validation.png)

@@

![Alt text](../Figures/posteriors_boxplots.png)

![Alt text](../Figures/posteriors_boxplots_A.png)

@@

![Alt text](../Figures/variance_decomposition.png)

@@

![Alt text](../Figures/scenario_extrapolation.png)

>>>>

## Parametric model
We defined a parametric model to consider all the three effects on respiration we hypothesized. The first is the influence of temperature, then the influence of soil moisture, and then a seasonal component which is assumed to be roughly proportional to the interactions of autotrophic respiration (which we hypothesized following a seasonal pattern).
Temperature and moisture scaling interact linearly, while seasonality was assumed additive:  
$$
Rh(t) =  \xi_{temp(t,j)} \cdot \xi_{moist(t,j)} + \xi_{sin(t,j)}
$$

@@

### Moisture 
The moisture scaling function had to be taken from a simplified version of Moyano (2013) in the SoilR package [@SierraMueller].
$$
\xi_{moist(t,k)} = a_j \cdot \theta_{v}(t) - b_j \cdot (\theta_{v}(t))^2
$$
Variance is by treatment.

@@

## Sites microclimate
![Climatic parameters measured at the sites, plotted as data density of all measurements. Not all times series cover the same period of time.](../Figures/climatedata.png){width=60%}

@@

![Alt text](../Figures/fit_ML_validation.png){width=80%}

![Alt text](../Figures/fit_model_validation.png){width=60%}

@@

![Alt text](../Figures/posteriors_boxplots.png){width=60%}

![Alt text](../Figures/posteriors_boxplots_A.png){width=60%}

@@

![Alt text](../Figures/variance_decomposition.png){width=60%}

![Alt text](../Figures/scenario_extrapolation.png){width=60%}

@@
